Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study in India

### 2025-09-01 manuscript.Rmd
Minor fixes in manuscript

##### Debojit Basak, MS `r insert_orcid_link("0000-0002-8378-9689")` <!-- Accepted, debojit88@gmail.com -->
Project Research Scientist, Institute of Post Graduate Medical Education and Research, Kolkata, India.

>>>>

##### Debojit Basak, MParm (DB) `r insert_orcid_link("0000-0002-8378-9689")` <!-- Accepted, debojit88@gmail.com -->
Project Research Scientist, Institute of Post Graduate Medical Education and Research, Kolkata, India.
